Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-03 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd

*What degree of flexibility is required from the model? Might the model need to be quickly reconfigured to explore new scenarios or problems proposed by clients / managers / model-users?* ***HF comment: love the inclusion of this question***

>>>>

*What degree of flexibility is required from the model? Might the model need to be quickly reconfigured to explore new scenarios or problems proposed by clients / managers / model-users?*
